Solving the Nonstationary Richards Equation\\ With Adaptive $hp$-FEM

### 2011-03-15 paper.tex
few little corrections...

It is well known that the $h$-based form~(\ref{rich-final}) 
of the Richards' equation is prone 
to errors in mass balance as well as to erroneous estimates of 
infiltration depth when inaccurate time integration is used (see, e.g., 
Celia et. al.~\cite{celia}). These errors are caused by improper discrete 
approximation of the time derivative term 
$C(h)\frac{\partial h}{\partial t}$ that originates in the mass (water content) derivative 
term $\frac{\partial \theta(h)}{\partial t}$. Kees et al.~\cite{kees-time-integ} have 
shown in the context of two-phase flow that higher-order time integration methods
can cure the mass balance problem.

>>>>

It is well known that the $h$-based form~(\ref{rich-final}) 
of the Richards equation is prone 
to errors in mass balance as well as to erroneous estimates of 
infiltration depth when inaccurate time integration is used (see, e.g., 
Celia et. al.~\cite{celia}). These errors are caused by improper discrete 
approximation of the time derivative term 
$C(h)\frac{\partial h}{\partial t}$ that originates in the mass (water content) derivative 
term $\frac{\partial \theta(h)}{\partial t}$. Kees et al.~\cite{kees-time-integ} have 
shown in the context of two-phase flow that higher-order time integration methods
can cure the mass balance problem.
